Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-26 ms.tex
Added a time series for Aug 14, 2016 made quickly with the same paramers as Aug 12, 2016.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830.}\label{fig:refCorrectedPhotAug12}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotAug12}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotAug12}
\end{centering}
\end{figure}
